Taking from the rich or giving to the poor: Evidence for a two-dimension measure of support for redistribution

### 2018-08-21 analysis/manuscript.Rmd
third trial
another change from local pc
trying github cloud to local pc
Intending to see if the local repositry changes when I work in the cloud
change from local pc to cloud
wflow_git_commit(all = TRUE)
Review intro, tables, and outlined discussion

---
title: "Taking from the rich or giving to the poor: Evidence for a two-dimension measure of support for redistribution"
date: "`r Sys.Date()`"
output:
  workflowr::wflow_html:
    toc: false
---

@@

# Introduction (1300 words aprox) change trial

## Mini intro (494 words)
[Problem]
The increasing levels of economic inequality have had a profound impact on societies. Indeed, more unequal countries tend to report worse indicators in well-being issues (e.g. health, security, education), than less unequal countries (Wilkinson & Pickett, 2015, 2017). To reduce economic inequality and its pernicious effects, more redistributive measurements are needed. That is,  to implement taxes and social transfer policies that redistribute resources within a society (OECD, 2014; World Inequality Report, 2017).

[Justification 1: different responses of redistribution]
Despite of the benefits of reducing economic inequality, and the general public desire to do so (Norton & Ariely, xxxx), support for redistribution is not always held by the public. Thus, though people might agree on having more effective government's actions to reduce economic inequality, they display a general aversion toward raising taxes (Bartels, 2005), or might disapprove government spending on social services (Fong, 2001).  Thus, support for redistribution is not only a general desire to reduce economic inequality, but also implies a procedural dimension regarding how to achieve such redistribution of resources. Indeed, McCall & Kenworthy (2009) posited that individuals might demand more government redistribution by implementing more transfers to the poorer, by raising taxes to the richer; or they might just desire other government actions aimed to reduce inequality of opportunity by providing more services like social insurance, labour regulations. In this vein.

[Justification 2: literature overrepresent a desire for, rather than how to redistribute]
However, empirical research use to operationalize support for redistribution by a single item that reflect the general desire for the government to reduce  economic inequality (e.g. *The government should reduce the income differences between those with higher incomes and those with lower incomes*), without saying anything about how to do so. Other indicators to operationalize support for redistribution focus on attitudes toward the welfare state (*references*), social spending (*references*), and behavior (*references*). Thus, researchers tend to use a quite diverse set of items to measure support for redistribution that might hamper direct comparison among indicators. Whilst people might agree that economic inequality should be reduced (desire), they might disagree about how to do so (procedures), which might reflect different dimensions of the same construct: a higher demand for redistribution among the well-off (taxes), or a higher provision for the worst-off (opportunities).

[Proposal: Aim of the paper]
The aim of this research is to provide empirical evidence about the dimensionality of support for redistribution. In line with McCall & Kenworthy (2009), we argue that support for redistribution can be focused on the role of the government to redistribute resources (e.g. progressive taxation); or on the provision of more opportunities to the disadvantaged (e.g. social spending). To this end, we conducted two studies. In study 1 we explored the dimensionality of the items that we collected from the literature. In study 2, we confirmed the two-dimension structure of the measure, and provide evidence about the relationship of each dimension to perceptions and ideologies of inequality.

@@

[Redistribution 1: Meanings]
From an economic perspective, redistribution can be defined as the use of tax and transfer policies aimed to reduce economic inequality (Luebker, 2014). This implies the distribution of benefits and taxes according to the economic position of taxpayers, which mean that redistribution becomes individually more expensive to the wealthy than to the poorer (Dimick, 2018). On the other hand, redistribution can be defined from an equality of opportunity perspective, which means that economic, social and cultural resources should be distributed in a way that equalizes the opportunities of everyone to get ahead (Roemer, 1998). In this sense, redistribution implies a level-the-playing field principle, by which outcomes will be determined by individual merit, not by individual background. However, redistribution implies both perspectives, since effective strategies to reduce economic inequalities demand integral and multidimensional government interventions aimed to provide more capabilities and resources to the public (see Atkinson, 2015).

[Redistribution 2: different from other related constructs - welfarism]
Support for redistribution is related to attitudes toward welfare state policies, but is not reducible to them. Redistributive policies represent a procedural mechanism that enhance aggregate welfare (Kelly & Enns, 2010); whereas welfare policies imply a whole institutional framework that articulates the responsibility of the government for a range and degree of social provision that redistribute income, risks and services (Mau, 2003). Thus, redistribution focuses on the allocation of means, goods, and opportunities in a given society, and represent a particular dimension of the welfare state (Roosma, 2012).

[Redistribution 3: dimensions]
Redistribution involves two separate propositions, a demanding side, related to redistributive voters preferences; and a supply side, related to the provision of public policies to meet people's demands (McCarthy & Pontusson, 2009). Individuals' support for redistribution is embedded in the demanding side, and can also reflect different dimensions according to how individuals think that resources should be distributed, that is, who should contribute to and benefit from redistribution (Zimmerman, 2016).  Thus, support for redistribution implies a procedural perspective about who should redistribute (e.g. the government), how to redistribute the resources (e.g. taxation, social spending), and who is going to benefit (e.g. all citizens, the disadvantaged).

@@

[Measurs of redistribution: indicators]
As shown in Table 1, there is a wide variety of indicators aimed to measure support for redistribution. Since there is no a validated measure of attitudes toward redistribution shared in the literature, researchers use single indicators that are widely used in international survey data. In our literature review, we found that measures of support for redistribution mainly stress the role of the government, whether to increase social spending, or by implementing a progressive taxation system. In addition, researchers also use other kind indicators to account for redistribution such as the general judgment about the current redistributive structure in a given context and the desired to change it; the general acceptance of economic inequality; the endorsement of specific social policies; or even by using left-right political ideology (see Table S1 at the supplementary material for full information of sources, topics, and items's wording).

[Measures of redistribution: overview and link to the aim of the research]
Considering the wide variety of indicators researchers use to measure support for redistribution, direct comparison among the literature can be challenging. However, McCall & Kenworthy (2009) propose that support for redistribution can be summarised as the endorsement of public policies aimed to redistribute economic resources, or as the government actions oriented to provide more opportunities to people in need. Thus, the aim of this study is to provide empirical evidence about this two-dimension structure of a measure of support for redistribution; and to show how each dimension is differently associated with a set of individual variables.

| Table 1. |  |  |  |
|---------------------------------------------------------------------------|----------------------------|-------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| Main topics of the indicators aimed to measure support for redistribution |  |  |  |
| Topic | Amount of coded indicators | Item's examples | Sources |
| Social spending | 119 | * Do you support more policies to increase the opportunities for children born in poor families and to foster more equality of opportunity, such as education policies?  (Alesina, 2018)* Government should increase benefits for the poorest, even if it means tax rises for everyone else (Bamfield & Horton, 2009)* Should social beneﬁts be cut in the future, should things stay as they are, or should social beneﬁts be extended? (Haack & Sieweke, 2017)* The government should provide a decent standard ofliving for the unemployed (ISSP, 2009; Steele, 2015; Kim & Lee, 2018) | Alesina (2018), Bamfield & Horton (2009), Boarini (2009), Fong (2001), Haack & Sieweke (2017), Kim & Lee (2018), Kteily et al. (2016), Laurin et al. (2013), Lierse (2018), Linos (2003), McCall et al. (2017), McCall Kenworthy (2009), McCarthy& Pontusson (2011), Pratto et al (1998), Rodriguez-Bailon et al. (2017) Scrugs & Hayes (2017), Shnabel et al. (2016), Steele (2015), van der Toorn (2015), van Oorschot & Meuleman (2012), Zimmerman & Reyna (2013), Encuesta Nacional COES - ENACOES (2016), Eurobarometer 72.1 Poverty social exclusion and economy (2010), Eurobarometer 74.1 (2013), Eurobarometer 81.5 (2015), General Social Survey (2015), International Social Justice Project - ISJP (2006), International Social Survey Programme - ISSP (2009) |
| Taxation | 63 | * Government should increase tax at the top to ensure they contribute more to public services (Bamfield & Horton, 2009)* Do you think people with high incomes should pay a larger share of their income in taxes than those with low incomes, the same share, or a smaller share? (ISSP, 2009; ENACOES, 2016; Kuhn, 2012, 2015)* The government should increase taxes to give more help to the poor. (McCall et al., 2017)* High-incomee earners should pay more tax than low income earners (Rodríguez-Bailón et al., 2017) | Alesina (2018), Bamfield & Horton (2009), Fong (2001), Kerr (2014), Kuhn (2012), Kuhn (2015), Kuzyemko et al (2015), Lierse (2018), McCall et al. (2017), McCall Kenworthy (2009), McCarthy& Pontusson (2011), Pratto et al (1998), Rodriguez-Bailon et al. (2017), Scrugs & Hayes (2017), Weakliem (2013), Zimmerman & Reyna (2013), Encuesta Nacional COES - ENACOES (2016), Eurobarometer 72.1 (2010), Eurobarometer 74.1 (2013), Eurobarometer 81.5 (2015), General Social Survey (2015), International Social Survey Programme - ISSP (2009), Latin American Public Opinion Project (2014), New Zealand Attitudes and Values Survey (2009-2018), Pew Research Center (2014) |
| Government role | 59 | * It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes (ISSP, 2009; Choi, 2018; Kim & Lee, 2018; McCall et al., 2017)* The government should take measures to reduce differences in income levels. (Dimick, 2018)* To reduce the inequality of opportunities between children born in poor and rich families, thegovernment has the ability and the tools to do: Nothing at all; Not much; Some; A lot (Alesina et al., 2018) | Alesina (2018), Bamfield & Horton (2009), Boarini (2009), Choi (2016), Dallinger (2010), Dimick (2018), Duman (2013), Fong (2001), Gimpelson & Treisman (2017), Gonthier (2016), Guillaud (2013),  Isakson (2009), Jaime-Castillo et al (2018), Jedinger (2018), Kerr (2014), Kim & Lee (2018), Kuhn (2009), Kuhn (2012), Kuhn (2015), Lierse (2018), Linos (2003), McCall et al. (2017), McCall Kenworthy (2009), Newman (2014), Page (2016), Rosma (2012), Schmidt-Catran (2014), Steele (2015), van Heuvelen (2017), van Oorschot & Meuleman (2012), Zimmerman & Reyna (2013), Encuesta Nacional COES - ENACOES (2016), Eurobarometer 72.1 (2010), Eurobarometer 74.1 (2013), Eurobarometer 81.5 (2015), European Social Survey Wave7 (2014), International Social Justice Project - ISJP (2006), International Social Survey Programme - ISSP (2009), Latin American Public Opinion Project (2014), Latinobarómetro (2013), World Values Survey (2012) |
| Redistribution structure | 36 | * Income distribution in Colombia should be more equitable (Coppini et al. 2018)* There is a need to redistribute wealth from the top to the bottom in this society (Kteily et al., 2016)* The (NATIONALITY)  Government should ensure that the wealth of the country is redistributed in a fair way to all citizens (Eurobarometer 74.1, 2013) | Coppini et al (2018), Fong (2001), Haack & Sieweke (2017), Jedinger (2018), Kteily et al. (2016), McCall et al. (2017), van Oorschot & Meuleman (2012), Encuesta Nacional COES - ENACOES (2016), Eurobarometer 72.1 (2010), Eurobarometer 74.1 (2013), International Social Justice Project - ISJP (2006) |
| Inequality acceptance | 16 | * Differences in income in [this country] are too large. (Dallinger, 2010)* Do you think that the fact that some people in the United States are rich and others are poor  represents a problem that needs to be ﬁxed or Is an acceptable part of our economic system? (Fong, 2001)* Inequality in the distribution of wealth is unjust. (McCall et al., 2017)* We need larger income differences as incentives for individual effort versus Incomes should be made more equal.  (Wulfgramm & Starke, 2016) | Bamfield & Horton (2009), Dallinger (2010), Fong (2001), Kerr (2014), Kuhn et al (2017), McCall et al. (2017), Page (2016), Rodriguez-Bailon et al. (2017), Wulfgramm & Starke (2016), Eurobarometer 72.1 (2010), Eurobarometer 74.1 (2013) |
| Social policies | 12 | Extent of agreement toward policies such as:* A tie-breaker policy in which a minority applicant is selected over a White applicant when the two applicants are equally qualified. (Lowery, 2007)* Wage subsidies, whereby the government pays employers to hire people from disadvantaged groups, to increase the number of jobs for low-skill workers (Rodríguez-Bailón et al., 2017) | Alesina (2018), Lowery (2007), Rodriguez-Bailon et al. (2017), Shnabel et al. (2016) |
| Political ideology | 1 | In political matters, people talk of left and right. How would you place your views on this scale, generally speaking? | Iglesias et al. (2013) |
| Note: |  |  |  |

@@

The aim of the current studies is to provide empirical evidence about the dimensionality of support for redistribution measurement. We argue that there are at least two different dimensions of support for redistribution, that might have different implications on how we conceptualize and operationalize the public preferences for redistribution. Researchers in social sciences usually use single-item indicators to measure support for redistribution; or include behavioral measures about how to redistribute resources (i.e. prosocial behavior, dictatorship paradigm, etc.). As suggested by McCall and McCarthy (2009) people might have different responses toward inequality, either by increasing the role of the government to reduce inequality; or by increasing other government actions oriented to provide people in need. Under this framework we compiled a set of indicators used in the literature to account for redistribution (see Table 1), and empirically modelled both factors. Then, in Study 1 we tested a set of 10 items related to different ways to measure redistribution, and conducted exploratory factor analysis to examine the factor structure of those items. In Study 2, we used the same indicators of support for redistribution in a different sample, and conducted confirmatory factor analysis to confirm that the dimensionality was held. In addition, we test the reliability of the measure and the association between dimensions of support for redistribution with individuals' ideologies.

@@

*Support for redistribution*: Participants completed a ten-item measure of support for redistribution (*M =* 5.21, *SD =* .85, alpha = .737) we constured based on the literature review about measurmens of redistribution. These items covered survey items usually used in the literature to operationalize support for redistribution (i.e. "The government should reduce income differences between the rich and the poor"), as well as related research that used different proxys indicators (e.g. welfare attitudes, preferences for progressive taxation and social spending). Respondents should rate their level of agreement with each statement on a 7-point scale ranging from 1 "strongly disagree" to 7 "strongly agree". Wording and descriptive statistics per item are presented in Table 2.

@@

We conducted a descriptive item analysis (mean, starndard deviation, and skewness) and tested the reliability of the measurement (overa Chronbach's alpha, alpha if deleted item, and item-test correlation). In  order to examine the dimensionality of the scale, we conducted an exploratory factor analysis using principal-axis factor extraction with Minimum Residual procedure (minres) and varimax rotation, supported by Lavaan package (Rosseel, 2012) implemented for R software.

@@

As can be seen in Table 2, most of the items mean-scores are over the technichal middle point of the scale (4), and are negatively skewed, which indicates that particpants scored mostly in the right  ("agreement") side of the scale. However, item 8 ("The government should increase taxes to provide more assistance to the most needed people") performed differently, since participants tended to disagree in this issue. Additionally, when examining the reliability measures of the scale, we got that the alpha if this item is deleted does not change (*alpha~if item-8 deleted~ =* .736) and this item reported the lowest correlation with the overall scale (*r~item8-scale~ =* .325). Apart from this item, all the items contributed appropriately to the realibility of the measurement and the item-test correlation.

| Table 2. |  |  |  |  |  |  |  |  |  |
|---------------------------------------------------------------------------------------------------------------------------------|------|------|-------|-------|---------|-------------------|-------------------|------|------|
| Item descriptive statistics and factor loadings |  |  |  |  |  |  |  |  |  |
| Item | Mean | SD | Skew | Rx-j | alpha-x | Factor 1 loadings | Factor 2 loadings | h2 | U2 |
| 6. Existe una gran necesidad de redistribuir la riqueza de aquellos que tienen m?s, hacia aquellos que tienen menos. | 5.19 | 1.71 | -0.85 | 0.680 | 0.686 | 0.69 | - | 0.55 | 0.45 |
| 1. El Gobierno tiene la responsabilidad de reducir las diferencias de ingresos entre los que tienen m?s y los que tienen menos. | 5.44 | 1.62 | -1.02 | 0.556 | 0.707 | 0.67 | - | 0.47 | 0.53 |
| 7. No hay ninguna necesidad de cambiar la distribuci?n de ingresos econ?micos en Colombia (r) | 6.3 | 1.13 | -2.11 | 0.396 | 0.726 | 0.49 | - | 0.24 | 0.76 |
| 4. El Gobierno deber?a imponer mayores impuestos a las personas con m?s ingresos econ?micos. | 5.44 | 1.67 | -1.04 | 0.459 | 0.716 | 0.38 | - | 0.21 | 0.79 |
| 10. El Gobierno deber?a hacer todo lo posible para mejorar las condiciones econ?micas de los grupos m?s desfavorecidos. | 6.17 | 1.13 | -1.79 | 0.551 | 0.711 | 0.45 | 0.32 | 0.30 | 0.70 |
| 3. El Gobierno deber?a gastar m?s dinero en subsidios para los pobres. | 4.06 | 1.8 | -0.12 | 0.389 | 0.727 | - | 0.64 | 0.41 | 0.59 |
| 9. Las personas con m?s riqueza deber?an ayudar m?s a las personas m?s necesitadas. | 5.49 | 1.5 | -1.01 | 0.511 | 0.709 | - | 0.46 | 0.29 | 0.71 |
| 5. Se deber?an reservar cupos en universidades para las personas m?s desfavorecidas. | 5.42 | 1.61 | -1 | 0.381 | 0.726 | - | 0.38 | 0.18 | 0.82 |
| 8. El gobierno deber?a incrementar los impuestos para dar m?s ayudas a las personas m?s necesitadas. | 3.28 | 1.79 | 0.38 | 0.325 | 0.736 | - | 0.36 | 0.14 | 0.86 |
| 2. El Gobierno deber?a proporcionar un nivel de vida decente a las personas que est?n desempleadas. | 5.31 | 1.46 | -0.85 | 0.512 | 0.710 | 0.35 | 0.35 | 0.25 | 0.75 |

The Parallel Analysis suggested a three-factor solution, but inspecting the screeplot and the underlying topic of the items, it seems clearer to retain a two-factor structure for the items about support for redistribution. Thus, Factor 1 represents the idea that the government should redistribute resources by increasing taxes;  and Factor 2, subscribes to the idea that the government should increase social spending and provide more assistance to people in need.

@@

#Parallel Analysis and Screeplot
fa.parallel(data1_redis_full[,c("Q1_red1","Q1_red2","Q1_red3","Q1_red4","Q1_red5","Q1_red6","Q1_red7_rec","Q1_red8","Q1_red9","Q1_red10")],
                        fm = 'minres', fa = 'fa')

@@

#EFA excluding item 2 and 10, better fit (*X^2^~(gl=13)~ =* 56.72, *p<* .001, *RMSEA =* .054; *TLI =* .929)
redis1_2_factor_b <- fa((data1_redis_full[,c("Q1_red1","Q1_red3","Q1_red4","Q1_red5","Q1_red6","Q1_red7_rec","Q1_red8","Q1_red9")]),
                                                nfactors = 2,rotate = "varimax",fm="minres")
#Print factor loadings (table 2)

@@

In Study 1, exploratory analyses provided us with evidence regarding the two-factor structure of pepole support for redistribution: either by endorsing the role of the government to redistribute and implement a progressive taxation system, or by increasing the social spending and assisting the disadvantaged. Thus, we decided to replicate these findings in a new sample, and provide further evidence of the implications of such dimensionality. The aim of Study 2 was to confirm the two-factor structure of the support for redistribution measurement, and test some of its associations with variables related to inequality justification, such as ideologies and socioeconomic status. This study is part of a broader project about perceptions of inequality and redistribution in Colombia.

@@

In Study 2, 1837 participants from eight universities along different regions of Colombia participated in a research about perceptions of inequality and redistribution (*M~age~ =* 21.99, *SD~age~ =* 5.46, 65.75% female; 81.24% were undergradutes, 11.49% were enrolled in work training, 3.73% reached up to high school, and 3.52% held postgraduate education).  Participants responded to an open call delivered by each university to participate in a study about social issues in Colombia. Participants were informed about the goals and conditions of the research and, if agreed in taking the study, they signed an informed consent and accessed to an online questionnaire. Data was collected during May 2018.

>>>>

behaviour---
title: "Taking from the rich or giving to the poor: Evidence for a two-dimension measure of support for redistribution"
date: "`r Sys.Date()`"
output:
  workflowr::wflow_html:
    toc: false
---

@@

# Introduction (1300 words aprox)

## Mini intro (494 words)
[Opening: importance of support for redistribution]
Given the pervasive and pernicious effects of economic inequality on societies wellbeing (Wilkinson & Pickett, 2015, 2017), redistribution gains more importance as one of the most effective ways of tackling economic inequality (OECD, 2014; World Inequality Report, 2017). To do so, redistribution use a set of taxes and social transfer policies through which different kind of resources are distributed among citizens (Luebker, 2014). However, the implementation of redistributive measurements is not just a default response of the governments but, under the assumption of a democratic system, it depends on citizens support for such public policies.

[Justification 1: different responses of redistribution]
Despite the general public desire to reduce economic inequality (Norton & Ariely, xxxx), support for redistribution is not always held by the public in the same way.  Though people might agree on having more effective government's actions to reduce economic inequality, they also tend to show a general aversion toward raising taxes (Bartels, 2005), or might disapprove government spending on social services (Fong, 2001). Thus, support for redistribution should not be reduced to a general desire for reducing economic inequality, but it needs an explicit procedural dimension regarding how to do so. Indeed, McCall & Kenworthy (2009) posited that individuals might demand more government redistribution by implementing more transfers to the poorer, by raising taxes to the richer; or they might just desire other government actions aimed to reduce inequality of opportunity by providing more services like social insurance, labour regulations.

[Justification 2: literature overrepresent a desire for, rather than how to redistribute]
However, empirical research tend to operationalize support for redistribution by a single item that reflect the general desire for the government to reduce  economic inequality (e.g. *The government should reduce the income differences between those with higher incomes and those with lower incomes*), without saying anything about how to do so. Other indicators to operationalize support for redistribution focus on attitudes toward the welfare state (*references*), social spending (*references*), and behavior (*references*). Thus, researchers tend to use a quite diverse set of items to measure support for redistribution that might hamper the comparison of findings. Whilst people might agree that economic inequality should be reduced (desire), they might disagree about how to do so (procedures), which might reflect different dimensions of the same construct: a higher demand for redistribution by taking more from the well-off (e.g. taxes), or by providing more opportunities for the worst-off (e.g. social insurance).

[Proposal: Aim of the paper]
The aim of this research is to examine the dimensionality of support for redistribution measures. In line with McCall & Kenworthy (2009), we argue that support for redistribution can be focused on the role of the government to redistribute resources (e.g. progressive taxation); or on the provision of more opportunities to the disadvantaged (e.g. social spending). To this end, we conducted two studies: in study 1 we explored the dimensionality of the items that we collected from the literature; and, in study 2, we confirmed the two-dimension structure of the measure, and provide evidence about the relationship of each dimension to perceptions and ideologies of inequality.

@@

[Redistribution 1: Meanings]
From an economic perspective, redistribution can be defined as the use of tax and transfer policies aimed to reduce economic inequality (Luebker, 2014). Thus, the redistribution of benefits and taxes according to the economic position of taxpayers become more individually expensive to the wealthy than to the poorer (Dimick, 2018). On the other hand, redistribution can be defined from an equality of opportunity perspective, which means that economic, social and cultural resources should be distributed in a way that equalizes the opportunities of everyone to get ahead (Roemer, 1998). In this sense, redistribution implies a level-the-playing field principle, by which outcomes will be determined by individual merit, not by individual background. Both perspectives are pivotal to reduce economic inequality, and do not compete to each other. In fact, effective strategies to reduce economic inequality demand a multidimensional government intervention aimed to provide more capabilities and resources to the public (see Atkinson, 2015).

[Redistribution 2: different from other related constructs - welfarism]
Though related, support for redistribution and attitudes toward welfare state policies are different constructs. Redistributive policies represent a procedural mechanism that enhance aggregate welfare (Kelly & Enns, 2010); whereas welfare policies imply a whole institutional framework that articulates the responsibility of the government for a range and degree of social provision that redistribute income, risks and services (Mau, 2003). Thus, redistribution is more specific, and focuses on the allocation of means, goods, and opportunities in a given society, and represent a particular dimension of the welfare state (Roosma, 2012).

[Redistribution 3: dimensions]
Additionally, redistribution involves two separate propositions, a demanding side, related to redistributive voters preferences; and a supply side, related to the provision of public policies to meet people's demands (McCarthy & Pontusson, 2009). Individuals' support for redistribution is embedded in the demanding side, and can also reflect different dimensions according to how individuals think that resources should be distributed, that is, who should contribute to and benefit from redistribution (Zimmerman, 2016).  Thus, support for redistribution implies a procedural perspective about who should redistribute (e.g. the government), how to redistribute the resources (e.g. taxation, social spending), and who is going to benefit (e.g. all citizens, the disadvantaged).

@@

[Measures of redistribution: indicators]
There are a wide variety of indicators aimed to measure support for redistribution. Since there is no a validated measure of attitudes toward redistribution shared in the literature, researchers use different ways to operationalize support for redistribution: indicators coming from international surveys that stress the responsibility of the government (e.g. "It is the responsibility of the government to reduce the differences in income between people with high incomes and those with low incomes", see ISSP, 2009); the role of the government to change redistributive structure (e.g. "The government should take measures to reduce differences in income levels" Dimick, 2018); the need to impose a progressive taxation system (e.g. "The government should increase taxes to give more help to the poor", McCall et al., 2017; "High-incomee earners should pay more tax than low income earners", Rodríguez-Bailón et al., 2017); the general acceptance about the current redistributive structure in a given context (e.g. "we need larger income differences as incentives for individual effort versus Incomes should be made more equal" Wulfgramm & Starke, 2016; "Differences in income in [this country] are too large." ISSP, 2009; Dallinger, 2010); or the endorsement of specific social policies (e.g. "Do you support more policies to increase the opportunities for children born in poor families and to foster more equality of opportunity, such as education policies?"  Alesina, 2018; "Should social beneﬁts be cut in the future, should things stay as they are, or should social beneﬁts be extended?" Haack & Sieweke, 2017); or even by using left-right political ideology (Iglesias et al., 2013) (see Table S1 at the supplementary material for full information items's wording for indicators that aim to measure support for redistribution).

[Measures of redistribution: overview and link to the aim of the research]
Considering the wide variety of indicators researchers use to measure support for redistribution, comparing the findings published in the literature could be challenging. However, McCall & Kenworthy (2009) propose that support for redistribution can be summarised as the endorsement of public policies aimed to redistribute economic resources, or as the government actions oriented to provide more opportunities to people in need. Thus, the aim of this study is to provide empirical evidence about this two-dimension structure of a measure of support for redistribution; and to show how each dimension is differently associated with a set of individual variables.

@@

The aim of the current studies is to provide empirical evidence about the dimensionality of support for redistribution measurement. We argue that there are at least two different dimensions of support for redistribution, that might have different implications on how we conceptualize and operationalize the public preferences for redistribution. Researchers in social sciences usually use single-item indicators to measure support for redistribution; or include behavioural measures about how to redistribute resources (i.e. prosocial behavior, dictatorship paradigm, etc.). As suggested by McCall and McCarthy (2009) people might have different responses toward inequality, either by increasing the role of the government to reduce inequality; or by increasing other government actions oriented to provide people in need. Under this framework we compiled a set of indicators used in the literature to account for redistribution (see Table 1), and empirically modelled both factors. Then, in Study 1 we tested a set of 10 items related to different ways to measure redistribution, and conducted exploratory factor analysis to examine the factor structure of those items. In Study 2, we used the same indicators of support for redistribution in a different sample, and conducted confirmatory factor analysis to confirm that the dimensionality was held. In addition, we test the reliability of the measure and the association between dimensions of support for redistribution with individuals' ideologies.

@@

*Support for redistribution*: Participants completed a ten-item measure of support for redistribution (*M =* 5.21, *SD =* .85, alpha = .737) we constured based on the literature review about measurmens of redistribution. These items covered survey items usually used in the literature to operationalize support for redistribution (i.e. "The government should reduce income differences between the rich and the poor"), as well as related research that used different proxys indicators (e.g. welfare attitudes, preferences for progressive taxation and social spending). Respondents should rate their level of agreement with each statement on a 7-point scale ranging from 1 "strongly disagree" to 7 "strongly agree". Wording of the items is shown in Table 1.

@@

We conducted a descriptive item analysis (mean, standard deviation, and skewness) and tested the reliability of the measurement (overall Chronbach's alpha, alpha if deleted item, and item-test correlation). In  order to examine the dimensionality of the scale, we conducted an exploratory factor analysis using principal-axis factor extraction with Minimum Residual procedure (minres) and varimax rotation, supported by Lavaan package (Rosseel, 2012) implemented for R software.

@@

As shown in Table 1, most of the items mean-scores are over the technical middle point of the scale (4), and are negatively skewed, which indicates that participants scored mostly in the right  ("agreement") side of the scale. However, participants tended to disagree in item 8 ("The government should increase taxes to provide more assistance to the most needed people"). Additionally, when examining the reliability measures of the scale, we got that the alpha if this item is deleted does not change (*alpha~if item-8 deleted~ =* .736) and this item reported the lowest correlation with the overall scale (*r~item8-scale~ =* .325). Apart from this item, all the items contributed appropriately to the reliability of the measurement.

| Table 1. |  |  |  |  |  |
|---------------------------------------------------------------------------------------------------------------------------------|------|------|-------|-------|---------|
| Descriptive statistics for items of support for redistribution |  |  |  |  |  |
| Item | Mean | SD | Skew | Rx-j | alpha-x |
| 6. Existe una gran necesidad de redistribuir la riqueza de aquellos que tienen más, hacia aquellos que tienen menos. | 5.19 | 1.71 | -0.85 | 0.680 | 0.686 |
| 1. El Gobierno tiene la responsabilidad de reducir las diferencias de ingresos entre los que tienen m?s y los que tienen menos. | 5.44 | 1.62 | -1.02 | 0.556 | 0.707 |
| 7. No hay ninguna necesidad de cambiar la distribución de ingresos econámicos en Colombia (r) | 6.3 | 1.13 | -2.11 | 0.396 | 0.726 |
| 4. El Gobierno debería imponer mayores impuestos a las personas con más ingresos econ?micos. | 5.44 | 1.67 | -1.04 | 0.459 | 0.716 |
| 10. El Gobierno debería hacer todo lo posible para mejorar las condiciones econ?micas de los grupos m?s desfavorecidos. | 6.17 | 1.13 | -1.79 | 0.551 | 0.711 |
| 3. El Gobierno debería gastar más dinero en subsidios para los pobres. | 4.06 | 1.8 | -0.12 | 0.389 | 0.727 |
| 9. Las personas con más riqueza deber?an ayudar m?s a las personas más necesitadas. | 5.49 | 1.5 | -1.01 | 0.511 | 0.709 |
| 5. Se deberían reservar cupos en universidades para las personas más desfavorecidas. | 5.42 | 1.61 | -1 | 0.381 | 0.726 |
| 8. El gobierno debería incrementar los impuestos para dar más ayudas a las personas más necesitadas. | 3.28 | 1.79 | 0.38 | 0.325 | 0.736 |
| 2. El Gobierno debería proporcionar un nivel de vida decente a las personas que están desempleadas. | 5.31 | 1.46 | -0.85 | 0.512 | 0.710 |
| Note: |  |  |  |  |  |

Although Parallel Analysis suggested a three-factor solution, both the screeplot and the underlying topic of the items, suggest a two-factor structure for the items about support for redistribution. Thus, Factor 1 represents the idea that the government should redistribute resources by increasing taxes;  and Factor 2, subscribes to the idea that the government should increase social spending and provide more assistance to people in need (see Table 2).

| Table 2. |  |  |  |  |
|---------------------------------------------------------------------------------------------------------------------------------|-------------------|-------------------|-------------|------------|
| Factor loadings, communality and uniqueness values for items of support for redistribution |  |  |  |  |
| Item | Factor 1 loadings | Factor 2 loadings | Communality | Uniqueness |
| 6. Existe una gran necesidad de redistribuir la riqueza de aquellos que tienen más, hacia aquellos que tienen menos. | 0.69 | - | 0.55 | 0.45 |
| 1. El Gobierno tiene la responsabilidad de reducir las diferencias de ingresos entre los que tienen m?s y los que tienen menos. | 0.67 | - | 0.47 | 0.53 |
| 7. No hay ninguna necesidad de cambiar la distribución de ingresos econámicos en Colombia (r) | 0.49 | - | 0.24 | 0.76 |
| 4. El Gobierno debería imponer mayores impuestos a las personas con más ingresos econ?micos. | 0.38 | - | 0.21 | 0.79 |
| 10. El Gobierno debería hacer todo lo posible para mejorar las condiciones econ?micas de los grupos m?s desfavorecidos. | 0.45 | 0.32 | 0.30 | 0.70 |
| 3. El Gobierno debería gastar más dinero en subsidios para los pobres. | - | 0.64 | 0.41 | 0.59 |
| 9. Las personas con más riqueza deberían ayudar más a las personas más necesitadas. | - | 0.46 | 0.29 | 0.71 |
| 5. Se deberían reservar cupos en universidades para las personas más desfavorecidas. | - | 0.38 | 0.18 | 0.82 |
| 8. El gobierno debería incrementar los impuestos para dar más ayudas a las personas más necesitadas. | - | 0.36 | 0.14 | 0.86 |
| 2. El Gobierno debería proporcionar un nivel de vida decente a las personas que están desempleadas. | 0.35 | 0.35 | 0.25 | 0.75 |
| Note: |  |  |  |  |

@@

#Parallel Analysis and Screeplot
#fa.parallel(data1_redis_full[,c("Q1_red1","Q1_red2","Q1_red3","Q1_red4","Q1_red5","Q1_red6","Q1_red7_rec","Q1_red8","Q1_red9","Q1_red10")],
#                        fm = 'minres', fa = 'fa')

@@

#EFA excluding item 2 and 10, better fit (*X^2^~(gl=13)~ =* 56.72, *p<* .001, *RMSEA =* .054; *TLI =* .929)
redis1_2_factor_b <- fa((data1_redis_full[,c("Q1_red1","Q1_red3","Q1_red4","Q1_red5","Q1_red6","Q1_red7_rec","Q1_red8","Q1_red9")]),
                                                nfactors = 2,rotate = "varimax",fm="minres")
#Print factor loadings (table 3)

@@

In Study 1, exploratory analyses provided us with evidence regarding the two-factor structure of people support for redistribution: either by endorsing the role of the government to redistribute and implement a progressive taxation system, or by increasing the social spending and assisting the disadvantaged. Thus, we decided to replicate these findings in a new sample, and provide further evidence of the implications of such dimensionality. The aim of Study 2 was to confirm the two-factor structure of the support for redistribution measurement, and test some of its associations with variables related to inequality justification, such as ideologies and socioeconomic status. This study is part of a broader project about perceptions of inequality and redistribution in Colombia.

@@

In Study 2, 1837 participants from eight universities along different regions of Colombia participated in a research about perceptions of inequality and redistribution (*M~age~ =* 21.99, *SD~age~ =* 5.46, 65.75% female; 81.24% were undergraduates, 11.49% were enrolled in work training, 3.73% reached up to high school, and 3.52% held postgraduate education).  Participants responded to an open call delivered by each university to participate in a study about social issues in Colombia. Participants were informed about the goals and conditions of the research and, if agreed in taking the study, they signed an informed consent and accessed to an online questionnaire. Data was collected during May 2018.
